---
title: "Wine Review World Map Project"
author: "Armistead, Vanessa; Pricken, Luisa; Roes, Bart; Rouatbi Ameni"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: cerulean
    highlight: tango 
---

```{r setup, echo=FALSE, include=FALSE}
# This is the chunck indicates all of the different packages used in our Rmd
library("leaflet")
library("geojsonio")
library("readr")
library("data.table")
library("purrr")
library("geonames")
library("tidyverse")
```

## Introduction 
We decided to work on a wine data review that was available on kaggle. This 
dataset contains information that can be found on the website
"Wine Enthousiast". We created an interactive map that is easy to navigate
through the different countries of the World. Indeed, we did not find any app or 
website that had a clear review of the wines throughout the World. With our map, 
one is able to see the average quality of the wine of each country, the most
common type of wine and the amount of wines that was review from each country.
Moreover, one can observe on the right side of the dashboard the "Wine data
explorer". One can change the variety of the wine and/or the country to see the 
relation between quality and price for the variety/varieties for the country/
countries. There is also an option on the dashboard to explore the data of wine
review. This allows you to search for a specific wine and receive all of the
important information such as the price or the winery. One can also vary the 
price range in order to find wines specific to everyone's willingness to pay. 

## Data Cleaning

#### Wine Review Dataset
The original dataset from kaggle contains 14 variables including: 
- X: this integer variable indicates the observation number
- Country: this variable shows from which country the wine comes from. It is 
of type character 
- Description: this variable of type character gives us information about the 
wine
- Designation: it indicates the vineyard of the winery. It is of type character
- Points: this interger variable contains the number of points that was given 
to the specific wine. The scale is between 1 and 100 where 100 indicates a good
wine
- Price: it indicates the cost of the different bottles of wine which is in 
US$. It is a numerical variable
- Province: this character variable shows from which province/state the wine
is from
- Region 1: it indicates the area of where the wine is from. It is of type
character
- Region 2: this character variables adds information about the region of the
wine
- Taster Name: character variable indicating the name of the taster of the wine
that posted the review on the website Wine Enthousiast
- Taster Twitter Handle: this character variables includes information about 
the Twitter account of the taster of the wine
- Title: it is a character variable that contains information about the wine 
such as the type of wine and the year of the wine
- Variety: this character variable indicates the grapes used for the wine for
instance "Pinot Gris"
- Winery: it is a character variable indicating which winery produced the wine

This dataset contains 129971 observations.

We then deleted the unnecessary variables, i.e. the X, the Taster Name, and the 
Taster Twitter Handle. Moreover, we deleted the rows containing missing
information about the price, the country, the variety and the number of points.
We aslo changed the names of the countries: United States of America and United
Kingdom so that they would match the names of our second database (i.e.
countries).
```{r cleaning, eval=FALSE, echo=FALSE}
# Download data
winemag <- read_csv("/Users/Vanessa/Desktop/winemag-data-130k-v2.csv")

# Take out unnecessary columns
winemag <- winemag[,-c(1,10,11)]

# Take out rows for wine without the price
winemag <- winemag[complete.cases(winemag[,5]),]

# Take out rows for wine without the points 
winemag <- winemag[complete.cases(winemag[,4]),]

# Take out rows for wine without the country 
winemag <- winemag[complete.cases(winemag[,1]),]

# Take out rows for wine without the variety 
winemag <- winemag[complete.cases(winemag[,10]),]

# Change country names to match the second dataset (countries)
winemag[which(winemag$country == "US"),]$country = "United States of America"
winemag[which(winemag$country == "England"),]$country = "United Kingdom"
```
This new database thus contains 12 variables and 101400 observations.

We then changed the format of the database into a RDA file so that people
could easily retrieve it when using our package. 
```{r RDA, eval=FALSE}
usethis::use_data(winemag, overwrite = TRUE)
```


#### Countries Dataset

In order to get information about the countries' coordinates in the World,
we used the geocountries function from the Geodata data package. This allowed 
us to create our World Map. 

```{r countries, eval=FALSE}
# Data from Geodata package
countries <- geojson_read("/Users/Vanessa/Desktop/countries.geojson", what = "sp")
```


#### Countries and Wine reviews databases 
In this part, we first needed to create a variable containing the value of the 
average points regarding the quality of the wines of the different countries. We
then joined it to the its respective countries in the database "countries".
After that, we wanted to know the number of unique countries and varieties in
our dataset. Moreover, we created new labels containing the most popular wine
and the total number of wines for each country. The results are displayed in the
map with different colors: the darker, the better

```{r, warning=FALSE, include=FALSE}
# Load the necessary data
load("../data/winemag.rda")
data <- winemag
load("../data/countries.rda")
```

```{r, warning=FALSE, eval=FALSE, include=FALSE}
# Calculate average wine quality per country
avg.quality <- data %>%
  group_by(country) %>%
  summarise(avg.quality = mean(points))


# Initialize matrix for label creation
df <- matrix(nrow = 255, ncol = 1, 0)
df <- as.data.frame(df)
df[,1] <- unique(countries$ADMIN)
colnames(df) <- c("country")
df$country <- as.character(df$country)
df <- df %>% left_join(avg.quality, by = c("country" = "country"))


# Find the number of unique countries/varieties that are present in the wine data
unique.countries <- unique(data$country)
unique.varieties <- unique(data$variety)


# Create a label based on the most popular wine
common_wines <- data %>%
  group_by(country, variety) %>%
  count()
wine.labels <- matrix(nrow = 42, ncol = 3)
wine.labels <- as.data.frame(wine.labels)
for(i in 1:42){
  a <- common_wines %>%
    filter(country == unique.countries[i]) 
  if (is.na(a) == FALSE) {
    wine.labels[i,] <- a[which.max(a$n),]
  }
}

wine.labels <- wine.labels[-43,]

df <- df %>% 
  left_join(wine.labels, by = c("country" = "V1"))

n.wines <- data %>%
  group_by(country) %>%
  count()

df <- df %>% left_join(n.wines, by = c("country" = "country"))

countries@data$quality<- df


# Creating colours for the graph

# Based on average quality
bins <- c()
for (i in 1:5) {
  bins[i] <- quantile(countries@data$quality$avg.quality, na.rm = T, probs = 0.2*i)
}
bins.avg <- c(80,round(bins,1),93)
pal.avg <- colorBin("YlOrRd", domain = countries$df,
                    bins = bins.avg)

# Based on number of wines 
bins <- c()
for (i in 1:5) {
  bins[i] <- quantile(countries@data$quality$n, na.rm = T, probs = 0.2*i)
}
bins.n <- c(0, bins, 60000)
pal.n <- colorBin("YlOrRd", domain = countries$df,
                  bins = bins.n)

pal.fun <- list(pal.avg,
                pal.avg,
                pal.n)
pal <- list(pal.avg(countries@data$quality$avg.quality), 
            pal.avg(countries@data$quality$avg.quality), 
            pal.n(countries@data$quality$n))
pal.name <- c(rep("Average wine quality",2),"Amount of wines")


# Change the countries database into an RDA file 
usethis::use_data(countries, overwrite = TRUE)
```



## Example of our Wine Review World Map

```{r connection}
m <- leaflet(countries) %>%
  setView(0, 0, 2) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('pk.eyJ1IjoiYmFydGozaCIsImEiOiJjam81amF6ODcwODBqM3FvYTlrN2E3azlvIn0.PUtXU40gLYiECsGAMzeYiw')))
```

```{r colors}
df <- matrix(nrow = 255,ncol = 1, 0)
df <- as.data.frame(df)

df[,1] <- unique(countries$ADMIN)
colnames(df) <- c("country")
df$country <- as.character(df$country)

df <- df %>% left_join(avg.quality, by = c("country" = "country"))

countries@data$quality <- df

bins <- c(84,85,86,87,88,89,90,91,92)
pal <- colorBin("YlOrRd", domain = countries$df,
                bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%g",
  df$country, df$avg.quality) %>% 
  lapply(htmltools::HTML)

m %>% addPolygons(
  fillColor = ~pal(df$avg.quality),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = "Average wine quality",
            position = "bottomleft")
```

This map shows us the average wine quality of each country in our database. The
darker the color, the better the quality. One can assess the exact average by 
moving the mouse on each different countries. For instance, the country with 
the highest average quality wine is the UK with the average of 91.55 and the
lowest is Ukraine with an average of 84.07. 


